\section{Expected Outcomes and Significance}
To evaluate the effectiveness of our work, as we mentioned in section
\ref{sec:ToolToAnalyze}, we can use a series of open-source test cases and benchmarks,
such as SPEC, UnixBench.
We will also consider using SGXGauge \cite{Kumar2022ACB}, a test suite specifically
designed to test the performance of trusted systems, to measure the performance
of our system.
Besides that, we are able to compare our system with other cross-platform TEEs.
For example, we can use HyperEnclave \cite{Jia2022HyperEnclaveAO}, TrustVisor
\cite{McCune2010TrustVisorET}, Occlum \cite{Shen2020OcclumSA} and Graphene
\cite{Tsai2017GrapheneSGXAP} as baseline systems for performance analysis.

Although these cross-platform TEEs propose various solutions to the legacy
software problem, most research involves modifying libraries and putting
them into the enclave.
This could lead to the expansion of the Trusted Computing Base (TCB)
and the attack surface's expansion.

Our solution uses binary rewriting to place the analyzed confidential code and data
into enclaves, hardening the legacy software and reducing the size of TCB.
We anticipate our system for general software can reach the following goals:
\begin{enumerate}[(1)]
    \item The analysis module can efficiently and accurately identify vulnerable code and data.
    Using analysis module alone can help developers find software weaknesses and flaws.
    \item The binary rewriting compiler can translate legacy software into enclave-protected programs
    with the help of analysis results.
    \item Our system is extended to support distributed programs.
    \item Based on the performance data, we design or modify the hardware.
    With hardware-assisted, we expect the performance can exceed other cross-platform TEEs
    or even approach the performance of native programs.
\end{enumerate}