\section{Study Schedule}
My PhD research will mainly focus on the study of general software migration in trusted computing systems.
To achieve these goals, my preliminary arrangement is as follows.
\begin{itemize}
    \item \nth{1} Year (2023-2024)
    \begin{enumerate}
        \item Complete the core courses and choose the elective courses
        that will help me with my research.
        \item Read the paper and design the whole system, while evaluating and revising
        our current ideas and plans.
    \end{enumerate}
    \item \nth{2} Year (2024-2025)
        \begin{enumerate}
            \item Start to implement our analysis and rewrite system based on
            first-year design.
            \item Submit the first top paper about our analysis module in OSDI/PLDI/ASPLOS.
        \end{enumerate}
    \item \nth{3} Year (2025-2026)
        \begin{enumerate}
            \item Modify and optimize our rewriting compiler.
            \item Extend our system to support distributed programs.
            \item Submit the second paper about our rewriting compiler in OSDI/PLDI/ASPLOS.
        \end{enumerate}
    \item \nth{4} Year (2026-2027)
        \begin{enumerate}
            \item Review our entire system and analyze their performance bottlenecks.
            \item Try to improve the performance of migrated programs by
            modifying the hardware.
            \item Submit the third paper about our work on software-hardware co-optimization in OSDI/PLDI/ASPLOS/MICRO.
            \item Complete the PhD graduation thesis.
        \end{enumerate}
\end{itemize}

